PANCHANGE_data_preprocessing

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
vectors with sum scores

```{r Check psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    autism_spectrum_disorder,
    autism_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
  ) %>%
    filter(autism_spectrum_disorder == "Autism spectrum disorder")
}
```

@@

### Controls
These individuals have no self report diagnosis of any kind that we measure. 
```{r mhd control}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

@@

## Total disorder count
```{r disorders_total_count}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric"
)

@@

Create new dataframe with the derived categories
```{r mhd categories}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
}
```

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_character_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_character_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_character_
  )
}
```

>>>>

```{r Check autism_spectrum_disorder}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    autism_spectrum_disorder,
    autism_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
  ) %>%
    filter(autism_spectrum_disorder == "Autism spectrum disorder")
}
```

@@

### Controls
These individuals have no self report diagnosis of any kind that we measure. 
```{r mhd control}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    autism_spectrum_disorder_numeric == "0" &
    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhd.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

@@

## Total disorder count
```{r disorders_total_count}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "autism_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric"
)

@@

Create new dataframe with the derived categories
```{r mhd categories}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    autism_spectrum_disorder_numeric,
    autism_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
}
```

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    autism_spectrum_disorder_numeric,
    autism_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_character_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_character_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_character_
  )
}
```
